% Document: CV

\documentclass[a4paper,10pt]{article}
\usepackage[none]{hyphenat}
\usepackage{array}
\usepackage[utf8]{inputenc}
\usepackage[margin=1cm]{geometry}
\geometry{a4paper}
\newcolumntype{L}{>{\raggedleft}p{0.15\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\begin{document}
\pagenumbering{gobble}
% Title centered in bold font
\begin{center}
\bf{\Huge{Alexandra Maguire}} \\[0.5cm]
\large Email: alm62@aber.ac.uk \\
\large Personal: alexandramaguire.co.uk \\
\large 500px: 500px.com/alexandramaguire\\
\large GitHub: github.com/alexandramaguire \\
\large About: about.me/alexandramaguire\\
\large LinkedIn: linkedin.com/pub/alex-maguire/a8/442/937\\[0.5cm]
\end{center}
\vspace{20pt}
% About section
\section*{About}
I am currently a second year student at Aberystwyth University studying for a BSc in Internet Computing and Systems Administration. I have a keen interest and appreciate website design, development and technologies. I am currently looking for an industrial placement for the upcoming year.
% Skill and achievements section
\section*{Skills and Achievements}
\begin{itemize}
    \item I have knowledge and experience of HTML5, CSS3, JavaScript and in developing websites
    \item I have experience in both Windows and Unix
    \item I am currently learning PHP and PostgreSQL
    \item  became a STEM ambassador which allowed me to run a code club to teach children between 11 and 12 years old how to use scratch. This allowed me to gain verbal communication skills and also team working skills as I worked with a partner for these lessons an hour every week
     \item I was awarded an Excellence Scholarship from Aberystwyth University 
     \item My first year average mark at University was a First (71.75 average mark)
\end{itemize}
% Education section
\section*{Education}
\begin{tabular}{L!{\VRule}R}
\\2013-2017&{\bf BSc in Internet Computing and Systems Administration, University of Aberystwyth, Wales. }\\[5pt]
&First Year Modules: 
Introduction to Computer Hardware, Operating Systems and Unix Tools (69) The Mathematics Driving License for Computer Science (69)
Introduction to Programming (78)
Chaos, Communications and Consciousness (73)
Professional and Personal Development (86)
Software Development (63)
Web Development Tools (71)
An Introduction to Communications and Telematics (68)\\
&Awards: Excellence Scholarship\\
\\
2011 - 2013&{\bf BTH Sixth Form, Altrincham, England.}\\[5pt]
&Information Communication Technology: (A) UCAS points: 120
Psychology: (B) UCAS Points: 100
Creative Media: Distinction UCAS points: 120\\
\\
2006 - 2011&{\bf BTH High School, Altrincham, England.}\\[5pt]
&10 GCSEs including: ICT (Distinction), English Literature(A), English Language(B), Science (B), Additional Science(B), Maths(C)
\end{tabular}
% Work experience section
\section*{Work Experience}
\begin{tabular}{L!{\VRule}R}
September 2012 - May 2013&{\bf Code Club Enrichment Co-Leader}\\[5pt]
&A I became a Stem Ambassador at the Museum of Science and Industry in Manchester. I helped run a weekly Code Club session with another student. My role was to prepare the sessions and make sure that the files for that session were uploaded so that the children could access them. I then helped run the children overcome their problems when they were doing the worksheets. I gained skills in working in a small team and also verbal communications skills.\\
\\
July 2012&{\bf Monk Marketing, Manchester, England }\\[5pt]
&Position: Work placement
During my first year of Sixth Form I had to take a two week work experience placement. My main role during this period was to create two websites with a partner which helped develop my team working skills. One website was for Monk Marketing Manchester and the other was for a separate project idea. I gained skills in using Dreamweaver, HTML and CSS.\\
\end{tabular}
% Interests section
\section*{Interests}
\begin{itemize}
\item I have taken a keen interest in photography, this is something I do in spare time. I enjoy going out and taking photos of different scenery. I have a recently created a 500px account which I upload my favourite photographs on and so that I can gain some inspiration from other peoples work. I update my Flickr Photostream regularly whenever I go out to take photographs.
\item Another interest of mine is reading fictional books. This helps me become more creative as a person and with my work especially when designing websites. Also I get a sense of enjoyment reading a series of books where the stories continue and you can see the progression of the different characters.
\item I also recently starting rowing with the rowing club in Borth. Rowing is helping me understand more how to work in a team as everyone in the boat has to work together as a team and timing is very important if you want it to be effective. Rowing has quickly became an interest of mine and is something I enjoy doing this in the afternoon or evening.  
\end{itemize}
% References section
\section*{References}
Dr Angharad Shaw, Teaching Fellow at  Aberystwyth University.\\
&Department of Computer Science, Llandinam Bldg, Penglais, Aberystwyth, Dyfed, SY23 3DB, Wales.\\
Email: ais@aber.ac.uk Phone: +44 (0)1970 622215\\
\\
Paul Reynolds, Business Owner\\    
& 11 Norley Drive, Sale Moor, Sale, Cheshire, M33 2JE\\
Email: paulreynolds@monkmarketing.com Phone: 0161-969995\\
\\
\end{document}
